SHAPR II: Dark Matter Substructure? Beware the Effect of Edge-on Disks

### 2015-08-28 papers/B1555_EdgeOn/B1555_letter.tex
syntext fixing
fix errors in paper text and reference

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
%SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
%Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
%Disks
SHAPR II: Dark Matter Substrcture? Beware the Effect of Edge-on Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. The free parameters of the model are, SIE: velocity dispersion ($\sigma$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$). Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
  We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE).

@@

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties. Positions are offsets from radio image component A measured in units of arcsec. The velocity dispersion $\sigma$ is in units of $km/s$. \textbf{$e$ is ellipticity defined as the axis ratio $q=1-e$ }and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & SIE & Expdisk 		   
\\
\hline
$x$  	  & $-0.1818 \pm 0.005$	&$-0.1472 \pm 0.005$ 	  \\
$y$	  &$-0.1988 \pm 0.005$	&$-0.2057 \pm 0.006$	 \\

$b$ &$0.21 \pm 0.01$  & ...   \\
$\kappa_0$ & ... & $0.11 \pm 0.01$        \\  
$e$	  & $0.31\pm 0.01$	&$0.87 \pm 0.01$ \\
$\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
$R_s$	& ...  & $0.28 \pm 0.01$\\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

>>>>

\title[Beware the Effect of Edge-on Disks]{
%Gravitational Lens Modelling of flux-ratio Anomalous System B1555+375
%SHARP II: Dark Matter Substructure, Gravitational Lens flux-ratio
%Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on
%Disks
SHAPR II: Dark Matter Substructure? Beware the Effect of Edge-on Disks
}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
jwhsueh@ucdavis.edu (JWH); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\\
$^{1}$Physics Dept., University of California, Davis, 1 Shields Ave.
Davis, CA 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

As a first trial of modelling, we create a single SIE model to check
the performance of a simple lensing potential. Consistent with
previous studies \citep{Marlow99, Xu14}, a single elliptical
potential model cannot \textbf{reproduce} the flux anomaly in B1555+375.
\textbf{The next step is to examine if an edge-on disk can cause similar perturbations in the strong lensing system  which results in flux ratio anomalies within the merging images. Among most of mass profiles, exponential disk profile best describes the disk component in spiral galaxies because it matches the light distribution of disk \citep{Kee98}. We thus choose a SIE plus exponential disk model (SIE+expdisk) in our study of B1555+375, focusing on the role of its edge-on disk in lens modelling. The free parameters of the model are, SIE: Einstein radius ($b$), centroid positions, ellipticity ($e$), and position angle ($\theta$); exponential disk: intrinsic central density ($\kappa_0$), centroid positions, ellipticity ($e$), position angle ($\theta$), and scale length ($R_d$). Detail definition of mass profiles in {\tt gravlens} can be found in \citet{Kee01}.}
  We have not included a third component such as an external
shear component or NFW halo into our model because the number of constraints provided by the
image positions and fluxes would not be sufficient to constrain such a
model. However, we note that the image not affected by dust (image C)
in the Keck AO data is consistent with negligible shear (i.e. shear
strength $\Gamma_s=0.002$), when modeled with the pixelized technique
of \citet{V09}.
%We then create two separate models of the lensing potential that both
%incorporate the disk.  In the first we treat the lens as a SIE bulge\textbf{/halo}
%and an exponential edge-on disk (SIE+expdisk). In the second model
%the disk is represented as a very elongated SIE component (2-SIE).

@@

\begin{table}
 \centering
% \begin{minipage}{140mm}
  \caption{Best-fit parameters of B1555+375 SIE+expdisk lens model and uncertainties. Positions are offsets from radio image component A measured in units of arcsec. The Einstein radius b is in unit of arcsec. $e$ is ellipticity defined as the axis ratio $q=1-e$ and $\theta$ is the position angle measured east of north.}
  \begin{tabular}{@{}ccc}
\hline 
 Parameter  & SIE & Expdisk 		   
\\
\hline
$x$  	  & $-0.1818 \pm 0.005$	&$-0.1472 \pm 0.005$ 	  \\
$y$	  &$-0.1988 \pm 0.005$	&$-0.2057 \pm 0.006$	 \\

$b$ &$0.21 \pm 0.01$  & ...   \\
$\kappa_0$ & ... & $0.11 \pm 0.01$        \\  
$e$	  & $0.31\pm 0.01$	&$0.87 \pm 0.01$ \\
$\theta$ &$2.96 \degr \pm 0.64 \degr$ &$7.00\degr \pm 0.70 \degr$ \\
$R_d$	& ...  & $0.28 \pm 0.01$\\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}
